%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Job title
    {AT\&T \normalfont{\hspace{.02 cm} | \hspace{.02 cm} Software Engineer}} % Organization
    {July 2020 - Present}% Location
    {} % Date(s)
    {
        \vspace{-4.0mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed over 600+ lines of NodeJS code to a local development tool used by several developers for "Handlebars" template syntax validation and streamlined a loading process that would ordinarily take hours over the course of a single day, yielding hours of saved development/labor costs and efficiency. Introduced an additional 300+ lines of code in Mocha unit testing to ensure code quality.}
        \item {Spearheaded the creation of a new Java/Maven/Apache Camel microservice totaling over 2600+ lines of code 
          that would be used for directing terabytes worth of data over the course of its lifetime to inform customer 
          segment marketing for att.com. Incorporated an additional 1200+ lines of Mockito unit testing code, and performed 
          stress-testing to ensure stability under various data loads.}
         \item {Proposed the practice of automated unit test generation using a tool called "EvoSuite" for a yearly innovation sprint and upon approval, was tasked with guiding its implementation among a team of 9 other engineers, resulting in high-coverage, low-overhead test suites that required significantly less time to produce when compared alongside their manually produced counterparts.}
        \item {Served as the local Community Engagement lead and helped organize several virtual volunteering/fundraising opportunities with organizations such as Feeding America and MakerGirl, achieving just over \$500 allocated towards various causes over the course of my service.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \vspace{-2.0mm}
  \cventry
    {} % Job title
    {The Home Depot \normalfont{\hspace{.02 cm} | \hspace{.02 cm} Software Engineer Intern}} % Organization
    {May 2019 - August 2019} % Location
    {} % Date(s)
    {
        \vspace{-4.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed 500+ lines of code to "Device Tracker", a React/Node.js application that would be used to locate 1000+ misplaced Android devices across hundreds of Home Depot retail locations, yielding hundreds of thousands of dollars in savings in labor and replacement costs.}
        \item {Initiated the development of "App360", a React/Node.js/MongoDB application that aimed to consolidate data on hundreds of Home Depot software applications, allowing directors, managers, and associates to communicate more effectively across teams and reduce redundancy in overlapping projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{-1.5mm}
  \cventry
    {} % Job title
    {RollOut Deliveries \normalfont{\hspace{.02 cm} | \hspace{.02 cm} Software Engineer Intern}} % Organization
    {May 2018 - August 2018} % Location
    {} % Date(s)
    {
    \vspace{-4.5mm}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achieved MVP peer-to-peer food delivery iOS/Swift application in a team consisting of 3 engineers over the course of 12 weeks, utilizing GoogleMaps API as the primary engine behind core functionality.}
        \item {Engineered end-to-end user registration, authentication, and payment flows to establish secure and reliable storage of user's personal information, utilizing Google Firebase as primary data layer and Stripe API for secure transactions.}
      \end{cvitems}
    }

\end{cventries}